---
title: "Extract metadata for GBIF Datasets"
author: "Lien Reyserhove"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

Load libraries:

```{r}
library(tidyverse)
library(lubridate)
library(janitor)
library(here)
library(rgbif)
```

Extract fields of interest:

```{r get_metadata}
alienCSI_dataset <- rgbif::datasets(uuid = "feb41318-374b-4ed6-b61e-0369993abedc")$data
```

Extract information:

```{r}
tibble(
  `title` = alienCSI_dataset$title,
  `type` =  alienCSI_dataset$type,
  `metadata language` = alienCSI_dataset$lang,
  `data language` = alienCSI_dataset$dataLanguage,
  `Update frequency` = alienCSI_dataset$maintenanceUpdateFrequency,
  `Data license` = alienCSI_dataset$license,
  `Description` = alienCSI_dataset$description,
  `Geographic Coverage - Description` = alienCSI_dataset$geographicCoverages[1],
  `Geographic Coverage - BoundBox` = alienCSI_dataset$geographicCoverages[2],
  `Taxonomic COverage - Description` = alienCSI_dataset$taxonomicCoverages[1],
  `Taxonomic coverage - Coverage` = alienCSI_dataset$taxonomicCoverages[2],
  `Temporal coverage - Type` = alienCSI_dataset$temporalCoverages[1],
  `Keyword Thesaurus` = alienCSI_dataset$keywordCollections$thesaurus,
  `Keyword List` = alienCSI_dataset$keywordCollections$keywords,
  `Project Data - Title` = alienCSI_dataset$project$title,
  `Project Data` = alienCSI_dataset$project$identifier
  
  
  ) %>% transpose()
```


#x	Basic metadata	Resource contacts: $data$contacts --> type = ADMINISTRATIVE_POINT_OF_CONTACT
#x	Basic metadata	Resource creators: --> type = ORIGINATOR
#x	Basic metadata	Metadata providers: --> type = METADATA_AUTHOR

x	Project Data	Title: $project$title
x	Project Data	Identifier: $project$identifier
x	Project Data	Description: $project$abstract
x	Project Data	Funding: $project$funding
x	Project Data	Study area description: $project$studyAreaDescription
x	Project Data 	Design description:  $project$designDescription
x	Project Data	Project Personel: $project$contacts
x	Sampling methods	Study extent: $samplingDescription$studyExtent
x	Sampling methods	Sampling description: $samplingDescription$sampling
x	Sampling methods	Quality control: $samplingDescription$qualityControl
x	Sampling methods	Step description: $samplingDescription$methodSteps
x	Citations	Resource citation: $citation$text
x	Citations 	Bibliographic citation: $bibliographicCitations (text)
x	Collection data	Collection Name: $collections
x	Colection data	Collection Identifier: $collections
x	Collection data	Parent collection identifier: $collections
x	External links	External links: $homepage
		Other data formats
	Additional metadata	Date created
	Additional metadata	Date last published
x	Additional metadata	Resource logo URL: $logoUrl
x	Additional metadata	Purpose: $purpose
x	Additional metadata	Maintenance description: $maintenanceDescription
	Additional metadata	Additional information
	Additional metadata	Alternative identifiers

